Out-of-Sample Comparisons of Overfit Models

### 2013-10-23 paper.tex
Make extremly minor tweak to wording in introduction
Add \ep and \eigen macros
This commit introduces some new macros that were helpful in editing Lemma 1's
proof.
- replaces the explicit use of \lambda with an \eigen operator.
- \varepsilon and bolded \varepsilon are pains to type, so we  introduces
  macros for them both.

@@

We focus on linear regression models for simplicity, but our basic
conclusions should be true for other models as well.  Under this
asymptotic theory, where the number of regressors $k$ increases with $T$
so that $\lim k/T$ is positive,
the \ols\ coefficient estimator is no longer
consistent or asymptotically normal \citep{Hub:73} and has positive
variance in the limit.  We show that, even so, the usual \oos\ average
is asymptotically normal and can consistently estimate the difference
between the models' generalization error, the expected loss in the
future conditional on the on the data available in period
$T$.\footnote{See, for example, \citet{HTF:08} for a discussion of
  generalization error.}  Under these asymptotics, the generalization
error does not converge to the expected performance of the pseudo-true
models, so existing in-sample and \oos\ comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our limit theory,
the model that is closer to the true \dgp\ in population can forecast
worse.  In such a situation, a standard in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an \oos\ comparison would correctly fail to reject the null that the
benchmark is more accurate.\footnote{In a pair of papers similar to
  ours, \citet{ClM:12,ClM:12b} study in-sample and \oos\ tests that
  the larger model has nonzero coefficients that are too close to zero
  to expect the model to forecast more accurately.  Like this paper,
  they argue that the larger model can be true but less accurate.
  However, they focus on an aspect of the \dgp\ that makes this
  phenomenon likely, while we focus on the coefficient estimates that
  produce less accurate forecasts.  Moreover, the implications of our
  asymptotic theories are different and their papers do not provide
  reasons to do \oos\ comparisons.}
Also note that, in this situation, a model that performs well
in-sample can perform badly out-of-sample \emph{even if there are no
structural breaks or other forms of instability.}  Researchers
have argued that a breakdown of in-sample forecasting ability
indicates a structural break (see \citealp{BoH:99} and
\citealp{StW:03}), but this breakdown can be caused by overfit as
well.

@@

\subsection{Notation and Forecasting Environment}
We assume the following forecasting environment. There are two
competing linear models that give forecasts for the target,
$y_{t+\h}$:
\[
y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}, \quad\text{and}\quad
y_{t+\h} = x_{2t}'\theta_2 + \varepsilon_{2,t+h};
\]
$t = 1,\dots,T-h$, $\h$ is the forecast horizon, and the
variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
Let
\begin{equation*}
  \mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)
\end{equation*}
with $x_t$ the vector of all elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$.  We will allow $K_1$ and $K_2$
to vary with $T$, so a stochastic array underlies all of our
asymptotic theory, but we suppress that notation to simplify the
presentation.

@@

Finally, define the following notation.  The $l_v$-norm for vectors in
$\Re^p$ (with $p$ arbitrary) is denoted $\lvert \cdot \rvert_v$, and
the $L_v$-norm for $L_v$-integrable random variables is $\lVert \cdot
\rVert_v$.  The functions $\lambda_i(\cdot)$ take a square-matrix
argument and return its $i$th eigenvalue (with $\lambda_{i}(A) \leq
\lambda_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
\infty$ unless stated otherwise.

@@

Assumption \ref{asmp-2} rules out uninteresting cases where the
forecast error vanishes.
\begin{asmp}\label{asmp-2}
  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
  positive and finite, and all of the eigenvalues of the covariance
  matrix of $x_t$ are uniformly positive and finite as well.  The
  Euclidean norms of the pseudo-true coefficients, $\theta_1$ and
  $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and $|\theta_2|_2 = O(1)$.
  Moreover, there exists a finite $\Delta$ such that $\| x_{it}'x_{it}
  \|_3 \leq K_i \Delta$,
  \begin{align*}
    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3} &\leq
    S_{T}\, \Delta, & \lVert
    \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
    \rVert_{3} &\leq S_{T}\, \Delta, \\
    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1})
    \rVert_{3} &\leq \Delta/S_{T}, & \lVert
    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3}
    &\leq \Delta/S_{T},
  \end{align*}
  for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
  1,2$,
  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
  \text{and} \qquad
  \ep{iT} = (\varepsilon_{i,1+\h}, \dots, \varepsilon_{i,T})'.\]
\end{asmp}

@@

Finally, we can look at the difference $\E_R \bar{D}_R - \E_T
\bar{D}_T$.  We can write this as
\begin{align*}
  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}^{R\prime}
  \hat{\theta}_{2R}^R - \hat{\theta}_{2T}^{T\prime}
  \hat{\theta}_{2T}^T \\ &=
  \mathbf{\varepsilon}_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \mathbf{\varepsilon}_T
\end{align*}
with $\tilde{X}_{2R}$ the $T \times K_2$ matrix $[X_{2R}'\ 0]'$.
Standard results for the moments of quadratic forms and of the
Inverse-Wishart distribution \citep{Haf:79} imply that
\begin{equation*}
  \E(\E_R \oosA - \E_T \oosB) = \frac{K_2 P}{(T - K_2 - 1)(R - K_2 - 1)}
\end{equation*}
and
\begin{align*}
  \var(\E_R & \oosA - \E_T \oosB) \\ &= \E
  \big[\tr((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1})\big]^2 + 2 \tr
  \E\big((X_{2R}'X_{2R})^{-2} - (X_{2T}'X_{2T})^{-2}\big) \\ &\quad - \big[\tr
  \E((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1}) \big]^2 \\ &=
  O(P/T)^2.
\end{align*}
So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$ only
if $P^3/T^2 \to 0$, which is slightly weaker than the general
requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the \oos\ average
still obeys the \mds\ \clt, but it is not centered correctly at $\E_T
\oosB$.

@@

Theorem~\ref{res:ftest} presents results for in-sample hypothesis
tests.
\begin{thm}\label{res:ftest}
  Suppose Assumptions 1--3 hold, that the models are nested, and that
  $L(e) = e^2$.  Also, let $\Lambda$ be a test statistic with nominal
  size $\alpha$ that has acceptance region contained in the set
  \[\{\hat{\theta}_T \mid (\hat{\theta}_T -
  \theta_0)'V_T(\hat{\theta}_T - \theta_0) < c \}\] for large enough
  $T$ and some $\theta_0$, $c$, and $V_T$, with $V_T$ a possibly
  random matrix with all eigenvalues uniformly bounded in probability
  and rank satisfying $\lim \rank(V_T)/T > 0$.  Then there exist
  distributions for $(x_t, \varepsilon_{t+h})$ such that
  \begin{equation}
    \label{eq:11}
    \Pr[\Lambda \text{ rejects} \mid \E_T \oosB \leq 0] \to^p 1
    \quad \text{as} \quad
    \theta'V_T\theta \to^p \infty \quad \text{($T$ is fixed)}
  \end{equation}
  for almost every sequence $\theta$ (a.e. with respect to Lebesgue
  measure) and 
  \begin{equation}
    \label{eq:15}
    \plim_{T \to \infty} \Pr[\Lambda \text{ rejects} \mid
    \E_T \oosB \leq 0] \geq \plim_{T \to \infty} \Pr[c + \delta < (\theta - \theta_0)' V_{T}
    (\theta - \theta_0) \mid \E_T \bar{D}_T \leq 0]
  \end{equation}
  for any $\delta > 0$.
\end{thm}
Note that, if $V_T$ is nonstochastic or converges in probability,
there are distributions on $(x_t, \varepsilon_{t+h})$ that are
compatible with~\eqref{eq:15} such that
\[\Pr[c + \delta < (\theta - \theta_0)'V_T (\theta - \theta_0) \mid
E_T \bar{D}_T \leq 0] \to^p 1
\]
for any $\theta \neq \theta_0$.  Otherwise, the rejection probability
will still depend on $\theta$ and $V_T$ and will typically be higher
than the nominal size of the test.

@@

\begin{cor}\label{res:ic}
  Suppose the conditions of Theorem~\ref{res:ftest} hold but that the
  statistic $\Lambda'$ is used for model selection; $\Lambda'$ selects
  the benchmark model for all $\hat{\theta}_T$ contained in a subset
  of the region
  \begin{equation*}
    \{\hat{\theta}_T \mid \hat{\theta}_T'V_T \hat{\theta}_T < c\}
  \end{equation*}
  and selects the alternative for all $\hat{\theta}_T$ outside that
  region.  Then there exist distributions on $x_t,\varepsilon_t$ such
  that
  \begin{equation}
    \label{eq:17}
    \plim \Pr[\Lambda' \text{ selects model 1} \mid \E_T \bar{D}_T \leq 0]
    \leq \plim \Pr[\theta_0'V_T \theta_0 < c \mid \E_T \bar{D}_T].
  \end{equation}
\end{cor}
As before, we often have 
\begin{equation*}
  \Pr[\theta_0'V_T \theta_0 < c \mid \E_T \bar{D}_T] \to^p 0.
\end{equation*}
Just as we saw with the $F$-test, adjusted $R$-squared, the \aic\ and
the \bic\ will only choose the benchmark model if $\hat{\theta}_T$
lies in the neighborhood of the cylinder defined by $\hat{\theta}_T
V_{T} \hat{\theta}_T = c$, regardless of which model is expected to
forecast better.  These statistics differ in how they determine the
size of the neighborhood, with the neighborhood shrinking slower for
the \bic\ than the \aic.

@@

\subsection{Setup}\label{sec:simulation-design}
The Monte Carlo experiment is intentionally very simple so that we can
isolate the influence of the models' complexity.  In particular, we do
not include some features that are common in forecasting
environments---serial dependence, heteroskedasticity, and complicated
\dgp s.  We simulate data for both studies from the equation
\begin{equation}\label{eq:6}
  y_t = x_t'\theta + \varepsilon_t,\quad \varepsilon_t \sim N(0,1),
  \quad t=1,\dots,T.
\end{equation}
The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
independent Standard Normal.  The benchmark model is
\begin{equation}
  \label{eq:1}
  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \varepsilon_t
\end{equation}
and the alternative model is the \dgp\ \eqref{eq:6}.  We let
$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
in its intended application as well as for more parsimonious models.
We let $T$ equal 100, 250, 500, or 1000.  We also vary $\theta$, and do 
so giving the benchmark and the alternative model comparable weight in
predicting $y_t$.  Specifically, we set
\begin{equation*}
  \theta_j = 
\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}  
\end{equation*}
with $c$ equal to zero or one.  When $c$ is one, we're more likely to
draw values of $X$ and $Y$ that make the estimated larger model more
accurate than the benchmark, and when $c$ is zero we're unlikely to
draw such values of $X$ and $Y$.  For all of the studies, $L(x) =
x^2$.

@@

We'll start with a very brief review.  \citet{GoW:08}
study the \oos\ forecasting performance of different variables thought
to predict the equity premium (calculated as the difference between
the return on the S\&P 500 index and the T-bill rate).  Some of these
variables are listed in
Table~\ref{tab:equity}.\footnote{Table~\ref{tab:equity} only lists the
  variables used in \citepos{GoW:08} ``kitchen sink''
  model.  Some of the variables that they use in bivariate models are
  excluded from this model either because the series are too short or
  because the variables are linear combinations of other variables.}
\citet{GoW:08} estimate the \oos\ forecasting
performance of bivariate models of the form
\[
r_{t+1} = \beta_0 + \beta_1 x_t + \varepsilon_{t+1}
\]
using \ols\ with a recursive window, where $r_{t+1}$ is the equity
premium and $x_t$ is a generic predictor, as well as some larger
models.  They find that these models forecast no better than the
prevailing mean of the equity premium.
\citet{CaT:08} find that nonlinear extensions of
Goyal and Welch's models are more accurate, either imposing sign
restrictions on the estimated coefficients or imposing that the
forecast be non-negative, but do not test for significance.

Obviously, \citepos{GoW:08} bivariate models do not
match the asymptotic theory of this paper, so we restrict our
attention here to their ``kitchen sink'' model, which includes all of
the variables, except for a few dropped because of data availability or
(perfect) multicollinearity.  Formally, the benchmark and alternative models are
\begin{eqnarray}
  \label{eq:3}
  r_{t+1} &=& \mu + \varepsilon_{1,t+1} \\
  \label{eq:2}
r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \varepsilon_{2,t+1}  
\end{eqnarray}
respectively and are estimated by \ols\ using the fixed-window scheme.
The predictors are listed in Table~\ref{tab:equity}; for a detailed
description of each predictor, please see Goyal and Welch's original
paper.  In this model, there are 13 regressors (including the constant
term) and we estimate the coefficients using annual data from 1928 to
2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
present results for one of \citepos{CaT:08}
restricted forecasting models.  For this model, we estimate
\eqref{eq:3} and \eqref{eq:2}, but impose that $\hat r_{t+1}$ be
non-negative for each forecast.  We then calculate the \oos\ test just
as for the unconstrained model.

@@

\textit{Equation~\eqref{eq:11}}: Note that a necessary condition for
$(\hat{\theta}_T - \theta_0)'V_T (\hat{\theta}_T - \theta_0) < c$
as $\theta'V_T\theta \to \infty$ is for all of the mass of
$\hat{\theta}_T$ to concentrate on the line joining $\theta$ and
$\theta_0$.  For any distribution of $(\varepsilon_{t+h}, x_t')$ such
that $\hat{\theta}_T$ depends on $\theta$ only through its mean, the
Lebesgue measure of parameter sequences satisfying this condition is
zero. \qed

\vspace{\baselineskip}
\noindent\textit{Equation~\eqref{eq:15}}:  Suppose that
$(\varepsilon_{t+h}, x_t) \sim i.i.d. N(0,I)$ and condition on $X_T$.
Then the distribution of $\hat{\theta}_{T}$ concentrates uniformly on
the ellipsoid
\begin{equation*}
  (\hat{\theta}_T - \theta)'(\hat{\theta}_T - \theta) = \theta'\theta.
\end{equation*}
Now, for $\theta$ and $V_T$ such that 
\begin{equation*}
  (\theta-\theta_0)' V_T (\theta-\theta_0) > c + \delta,
\end{equation*}
the probability that $\hat{\theta}_T$ is inside the acceptance region
of the test is less than $(1/2)^{K_2}$, which converges to zero as $T
\to \infty$. \qed

>>>>

\newcommand{\e}{\varepsilon}
\newcommand{\eb}{\mathbf{\e}}
\DeclareMathOperator{\eigen}{\lambda}

@@

We focus on linear regression models for simplicity, but our basic
conclusions should be true for other models as well.  Under this
asymptotic theory, where the number of regressors $k$ increases with $T$
so that $\lim k/T$ is positive,
the \ols\ coefficient estimator is no longer
consistent or asymptotically normal \citep{Hub:73} and has positive
variance in the limit.  We show that, even so, the usual \oos\ average
is asymptotically normal and can consistently estimate the difference
between the models' generalization error, the expected loss in the
future conditional on the on the data available in period
$T$.\footnote{See, for example, \citet{HTF:08} for a discussion of
  generalization error.}  Under these asymptotics, the generalization
error does not converge to the expected performance of the pseudo-true
models, so existing in-sample and \oos\ comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our limit theory,
the model that is closer to the true \dgp\ in population can forecast
worse.  In such a situation, a standard in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an \oos\ comparison would correctly fail to reject the null that the
benchmark is more accurate.\footnote{In a pair of papers similar to
  ours, \citet{ClM:12,ClM:12b} study in-sample and \oos\ tests that
  the larger model has nonzero coefficients that are too close to zero
  to expect the model to forecast more accurately.  Like this paper,
  they argue that the larger model can be true but less accurate.
  However, they focus on an aspect of the \dgp\ that makes this
  phenomenon likely, while we focus on the coefficient estimates that
  produce less accurate forecasts.  Moreover, the implications of our
  asymptotic theories are different and their papers do not provide
  reasons to do \oos\ comparisons.}
Also note that, in this situation, a model that performs well
in-sample can perform badly out-of-sample \emph{even if there are no
structural breaks or other forms of instability.}  Researchers
have argued that a breakdown of in-sample forecasting ability
indicates a structural break (see \citealp{BoH:99} and
\citealp{StW:03} among others), but this breakdown can be caused by overfit as
well.

@@

\subsection{Notation and Forecasting Environment}
We assume the following forecasting environment. There are two
competing linear models that give forecasts for the target,
$y_{t+\h}$:
\[
y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
\]
$t = 1,\dots,T-h$, $\h$ is the forecast horizon, and the
variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
Let
\begin{equation*}
  \mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)
\end{equation*}
with $x_t$ the vector of all elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$.  We will allow $K_1$ and $K_2$
to vary with $T$, so a stochastic array underlies all of our
asymptotic theory, but we suppress that notation to simplify the
presentation.

@@

Finally, define the following notation.  The $l_v$-norm for vectors in
$\Re^p$ (with $p$ arbitrary) is denoted $\lvert \cdot \rvert_v$, and
the $L_v$-norm for $L_v$-integrable random variables is $\lVert \cdot
\rVert_v$.  The functions $\eigen_i(\cdot)$ take a square-matrix
argument and return its $i$th eigenvalue (with $\eigen_{i}(A) \leq
\eigen_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
\infty$ unless stated otherwise.

@@

Assumption \ref{asmp-2} rules out uninteresting cases where the
forecast error vanishes.
\begin{asmp}\label{asmp-2}
  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
  positive and finite, and all of the eigenvalues of the covariance
  matrix of $x_t$ are uniformly positive and finite as well.  The
  Euclidean norms of the pseudo-true coefficients, $\theta_1$ and
  $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and $|\theta_2|_2 = O(1)$.
  Moreover, there exists a finite $\Delta$ such that $\| x_{it}'x_{it}
  \|_3 \leq K_i \Delta$,
  \begin{align*}
    \lVert \eigen_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3} &\leq
    S_{T}\, \Delta, & \lVert
    \eigen_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
    \rVert_{3} &\leq S_{T}\, \Delta, \\
    \lVert \eigen_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1})
    \rVert_{3} &\leq \Delta/S_{T}, & \lVert
    \eigen_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3}
    &\leq \Delta/S_{T},
  \end{align*}
  for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
  1,2$,
  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
  \text{and} \qquad
  \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
\end{asmp}

@@

Finally, we can look at the difference $\E_R \bar{D}_R - \E_T
\bar{D}_T$.  We can write this as
\begin{align*}
  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}^{R\prime}
  \hat{\theta}_{2R}^R - \hat{\theta}_{2T}^{T\prime}
  \hat{\theta}_{2T}^T \\ &=
  \eb_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \eb_T
\end{align*}
with $\tilde{X}_{2R}$ the $T \times K_2$ matrix $[X_{2R}'\ 0]'$.
Standard results for the moments of quadratic forms and of the
Inverse-Wishart distribution \citep{Haf:79} imply that
\begin{equation*}
  \E(\E_R \oosA - \E_T \oosB) = \frac{K_2 P}{(T - K_2 - 1)(R - K_2 - 1)}
\end{equation*}
and
\begin{align*}
  \var(\E_R & \oosA - \E_T \oosB) \\ &= \E
  \big[\tr((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1})\big]^2 + 2 \tr
  \E\big((X_{2R}'X_{2R})^{-2} - (X_{2T}'X_{2T})^{-2}\big) \\ &\quad - \big[\tr
  \E((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1}) \big]^2 \\ &=
  O(P/T)^2.
\end{align*}
So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$ only
if $P^3/T^2 \to 0$, which is slightly weaker than the general
requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the \oos\ average
still obeys the \mds\ \clt, but it is not centered correctly at $\E_T
\oosB$.

@@

Theorem~\ref{res:ftest} presents results for in-sample hypothesis
tests.
\begin{thm}\label{res:ftest}
  Suppose Assumptions 1--3 hold, that the models are nested, and that
  $L(e) = e^2$.  Also, let $\Lambda$ be a test statistic with nominal
  size $\alpha$ that has acceptance region contained in the set
  \[\{\hat{\theta}_T \mid (\hat{\theta}_T -
  \theta_0)'V_T(\hat{\theta}_T - \theta_0) < c \}\] for large enough
  $T$ and some $\theta_0$, $c$, and $V_T$, with $V_T$ a possibly
  random matrix with all eigenvalues uniformly bounded in probability
  and rank satisfying $\lim \rank(V_T)/T > 0$.  Then there exist
  distributions for $(x_t, \e_{t+h})$ such that
  \begin{equation}
    \label{eq:11}
    \Pr[\Lambda \text{ rejects} \mid \E_T \oosB \leq 0] \to^p 1
    \quad \text{as} \quad
    \theta'V_T\theta \to^p \infty \quad \text{($T$ is fixed)}
  \end{equation}
  for almost every sequence $\theta$ (a.e. with respect to Lebesgue
  measure) and 
  \begin{equation}
    \label{eq:15}
    \plim_{T \to \infty} \Pr[\Lambda \text{ rejects} \mid
    \E_T \oosB \leq 0] \geq \plim_{T \to \infty} \Pr[c + \delta < (\theta - \theta_0)' V_{T}
    (\theta - \theta_0) \mid \E_T \bar{D}_T \leq 0]
  \end{equation}
  for any $\delta > 0$.
\end{thm}
Note that, if $V_T$ is nonstochastic or converges in probability,
there are distributions on $(x_t, \e_{t+h})$ that are
compatible with~\eqref{eq:15} such that
\[\Pr[c + \delta < (\theta - \theta_0)'V_T (\theta - \theta_0) \mid
E_T \bar{D}_T \leq 0] \to^p 1
\]
for any $\theta \neq \theta_0$.  Otherwise, the rejection probability
will still depend on $\theta$ and $V_T$ and will typically be higher
than the nominal size of the test.

@@

\begin{cor}\label{res:ic}
  Suppose the conditions of Theorem~\ref{res:ftest} hold but that the
  statistic $\Lambda'$ is used for model selection; $\Lambda'$ selects
  the benchmark model for all $\hat{\theta}_T$ contained in a subset
  of the region
  \begin{equation*}
    \{\hat{\theta}_T \mid \hat{\theta}_T'V_T \hat{\theta}_T < c\}
  \end{equation*}
  and selects the alternative for all $\hat{\theta}_T$ outside that
  region.  Then there exist distributions on $x_t,\e_t$ such
  that
  \begin{equation}
    \label{eq:17}
    \plim \Pr[\Lambda' \text{ selects model 1} \mid \E_T \bar{D}_T \leq 0]
    \leq \plim \Pr[\theta_0'V_T \theta_0 < c \mid \E_T \bar{D}_T].
  \end{equation}
\end{cor}
As before, we often have 
\begin{equation*}
  \Pr[\theta_0'V_T \theta_0 < c \mid \E_T \bar{D}_T] \to^p 0.
\end{equation*}
Just as we saw with the $F$-test, adjusted $R$-squared, the \aic\ and
the \bic\ will only choose the benchmark model if $\hat{\theta}_T$
lies in the neighborhood of the cylinder defined by $\hat{\theta}_T
V_{T} \hat{\theta}_T = c$, regardless of which model is expected to
forecast better.  These statistics differ in how they determine the
size of the neighborhood, with the neighborhood shrinking slower for
the \bic\ than the \aic.

@@

\subsection{Setup}\label{sec:simulation-design}
The Monte Carlo experiment is intentionally very simple so that we can
isolate the influence of the models' complexity.  In particular, we do
not include some features that are common in forecasting
environments---serial dependence, heteroskedasticity, and complicated
\dgp s.  We simulate data for both studies from the equation
\begin{equation}\label{eq:6}
  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
  \quad t=1,\dots,T.
\end{equation}
The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
independent Standard Normal.  The benchmark model is
\begin{equation}
  \label{eq:1}
  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
\end{equation}
and the alternative model is the \dgp\ \eqref{eq:6}.  We let
$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
in its intended application as well as for more parsimonious models.
We let $T$ equal 100, 250, 500, or 1000.  We also vary $\theta$, and do 
so giving the benchmark and the alternative model comparable weight in
predicting $y_t$.  Specifically, we set
\begin{equation*}
  \theta_j = 
\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}  
\end{equation*}
with $c$ equal to zero or one.  When $c$ is one, we're more likely to
draw values of $X$ and $Y$ that make the estimated larger model more
accurate than the benchmark, and when $c$ is zero we're unlikely to
draw such values of $X$ and $Y$.  For all of the studies, $L(x) =
x^2$.

@@

We'll start with a very brief review.  \citet{GoW:08}
study the \oos\ forecasting performance of different variables thought
to predict the equity premium (calculated as the difference between
the return on the S\&P 500 index and the T-bill rate).  Some of these
variables are listed in
Table~\ref{tab:equity}.\footnote{Table~\ref{tab:equity} only lists the
  variables used in \citepos{GoW:08} ``kitchen sink''
  model.  Some of the variables that they use in bivariate models are
  excluded from this model either because the series are too short or
  because the variables are linear combinations of other variables.}
\citet{GoW:08} estimate the \oos\ forecasting
performance of bivariate models of the form
\[
r_{t+1} = \beta_0 + \beta_1 x_t + \e_{t+1}
\]
using \ols\ with a recursive window, where $r_{t+1}$ is the equity
premium and $x_t$ is a generic predictor, as well as some larger
models.  They find that these models forecast no better than the
prevailing mean of the equity premium.
\citet{CaT:08} find that nonlinear extensions of
Goyal and Welch's models are more accurate, either imposing sign
restrictions on the estimated coefficients or imposing that the
forecast be non-negative, but do not test for significance.

Obviously, \citepos{GoW:08} bivariate models do not
match the asymptotic theory of this paper, so we restrict our
attention here to their ``kitchen sink'' model, which includes all of
the variables, except for a few dropped because of data availability or
(perfect) multicollinearity.  Formally, the benchmark and alternative models are
\begin{eqnarray}
  \label{eq:3}
  r_{t+1} &=& \mu + \e_{1,t+1} \\
  \label{eq:2}
r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \e_{2,t+1}  
\end{eqnarray}
respectively and are estimated by \ols\ using the fixed-window scheme.
The predictors are listed in Table~\ref{tab:equity}; for a detailed
description of each predictor, please see Goyal and Welch's original
paper.  In this model, there are 13 regressors (including the constant
term) and we estimate the coefficients using annual data from 1928 to
2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
present results for one of \citepos{CaT:08}
restricted forecasting models.  For this model, we estimate
\eqref{eq:3} and \eqref{eq:2}, but impose that $\hat r_{t+1}$ be
non-negative for each forecast.  We then calculate the \oos\ test just
as for the unconstrained model.

@@

\textit{Equation~\eqref{eq:11}}: Note that a necessary condition for
$(\hat{\theta}_T - \theta_0)'V_T (\hat{\theta}_T - \theta_0) < c$
as $\theta'V_T\theta \to \infty$ is for all of the mass of
$\hat{\theta}_T$ to concentrate on the line joining $\theta$ and
$\theta_0$.  For any distribution of $(\e_{t+h}, x_t')$ such
that $\hat{\theta}_T$ depends on $\theta$ only through its mean, the
Lebesgue measure of parameter sequences satisfying this condition is
zero. \qed

\vspace{\baselineskip}
\noindent\textit{Equation~\eqref{eq:15}}:  Suppose that
$(\e_{t+h}, x_t) \sim i.i.d. N(0,I)$ and condition on $X_T$.
Then the distribution of $\hat{\theta}_{T}$ concentrates uniformly on
the ellipsoid
\begin{equation*}
  (\hat{\theta}_T - \theta)'(\hat{\theta}_T - \theta) = \theta'\theta.
\end{equation*}
Now, for $\theta$ and $V_T$ such that 
\begin{equation*}
  (\theta-\theta_0)' V_T (\theta-\theta_0) > c + \delta,
\end{equation*}
the probability that $\hat{\theta}_T$ is inside the acceptance region
of the test is less than $(1/2)^{K_2}$, which converges to zero as $T
\to \infty$. \qed
